### 2022-10-14 manuscript.Rmd
Add text for control analysis for TFR

>>>>

Finally, we had wondered if the reduction in alpha/beta power might merely reflect differences in the timing of motor preparation between conditions, given the well-established link between motor processes and beta power over sensorimotor cortex [@kivalik2013].
To rule this out, we extracted single trial percent signal change based on the distribution of clusters from the permutation tests (time window 600–1,200 ms, frequency range 8–20 Hz, electrodes P3, Pz, P4, PO3, POz, and PO4; see Figures 3 and 4).
We then subjected these to a linear-mixed effects model that controlled for log-transformed reaction time as a covariate of no interest.
This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.
